---
title: "R Notebook"
output: html_notebook
---
```{r}
library(countrycode)
library(stargazer)
library(httr)
```

# Data

* I find a happiness index data from https://www.kaggle.com/datasets/unsdsn/world-happiness?select=2019.csv
* I am also going to use the World Bank from class

```{r}
# data loading
happy19 <- read.csv("data/2019.csv")
wb <- read.csv("data/WB_Emissions.csv")
```

# Data Cleaning

## world bank data

* The objective here is cleaning the world bank data. Some of the process are same as the class lecture, but I filter the data to only 2019 because the happiness data is from 2019.

```{r}
# change variable names of world bank data
colnames(wb)[5] = "NO2"
colnames(wb)[6] = "CO2"
colnames(wb)[7] = "CH4"
```

```{r}
# we only need the 2019 data from world bank 
# because I only have 2019 happiness index
wb = wb[which(wb$Time == 2019),]
```

```{r}
# change variables to numerical in world bank data
wb[c("CO2", "NO2", "CH4")] = lapply(wb[c("CO2", "NO2", "CH4")], as.numeric)

# only select the columns I want from world bank
wb = wb[c("Country.Code", "CO2", "NO2", "CH4")] 
```

```{r}
# delete na observations
wb = na.omit(wb) 
```

## happiness data

```{r}
# Renaming long or confusing columns
colnames(happy19)[6] = "life"
colnames(happy19)[7] = "freedom"
colnames(happy19)[9] = "corruption"
```

```{r}
# Getting rid of unnecessary columns
happy19 = happy19[,-c(1)]
```

```{r}
# Dealing with missing data
happy19 = na.omit(happy19) 
```

```{r}
# create a country code for happiness data
happy19$Country.code = countrycode(happy19$Country.or.region, "country.name", "iso3c")
```

# Merge the data

* merge by country code

```{r}
# merge the data set
df = merge(happy19,wb, by.x = "Country.code", by.y = "Country.Code")
```

* check which countries did not get a match from happiness data 

```{r}
# check which country did not get a match
setdiff(happy19$Country.or.region, df$Country.or.region)
```

* after manual investigation. the above four regions are not in world data data set.

# running a simple regression

## first make some EDA plots

```{r}
#Scatter plot
plot(df$NO2,df$Score)
plot(df$CO2,df$Score)
plot(df$CH4,df$Score)
```

* looks like there is no relationship between emission and happiness score

## run the regression

```{r}
#Regression model
m1 = lm(Score~CO2, data = df)
summary(m1)
m2 = lm(Score~NO2, data = df)
summary(m2)
m3 = lm(Score~CH4, data = df)
summary(m3)
```

* All three emmision levels has no relationship with happiness

## output result by stargazer
```{r}
#Output Regression
stargazer(m1,m2,m3, type = "html", out = "model.html")
BROWSE("model.html")
```

